The Spine of American Law: Digital History Methods and U.S. Legal Practice

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Remove author identifier in a meaningless gesture towards double blind peer review

---
author:
- Kellen Funk
- Lincoln Mullen
fontfamily:
- mathpazo
fontsize: 12pt
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
  word_document: 
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    pandoc_args: ["--smart"]
title: "The Spine of American Law: Digital History Methods and U.S. Legal Practice"
---

>>>>

---
author:
fontfamily:
- mathpazo
fontsize: 12pt
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
  word_document: 
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    pandoc_args: ["--smart"]
title: "The Spine of American Law: Digital History Methods and U.S. Legal Practice"
---
